Paper Analysis

### 2025-05-06 Paper_WriteUp/Paper_Plots.qmd
fixing figS3 chunk

```{r figure S3 left}
## global effects first
data_path <- here("results_2025/lichess1700-1900")

fit_17_19_bullet_5 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_n5.RDS"))

fit_17_19_bullet_10 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_n10.RDS"))

@@

@@

```{r figure S3 right}
## global effects first
data_path <- here("results_2025/lichessGrandmasters")

fit_gm_bullet_5 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_n5.RDS"))

fit_gm_bullet_10 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_n10.RDS"))

>>>>

```{r figure S3 left}
model_path = here("results_revision", "lichess1700-1900")

#GM n = 1 model
fit_17_19_bullet_prev = readRDS(file = here(model_path, "all_rated_bullet_model_n1.RDS"))

#GM n = 5 model
fit_17_19_bullet_5 = readRDS(file = here(model_path, "all_rated_bullet_model_n5.RDS"))

#GM n = 10 model
fit_17_19_bullet_10 = readRDS(file = here(model_path, "all_rated_bullet_model_n10.RDS"))

@@

hist_comp_global <- bind_rows(prev_pars, pre_5_pars, pre_10_pars) |> 
  ggplot(aes(x = value, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(n.breaks = 3) +
  scale_color_viridis_d(option = "H")

@@

```{r figure S3 right}
model_path = here("results_revision", "lichessGrandmasters")

#GM n = 5 model
fit_gm_bullet_5 = readRDS(file = here(model_path, "all_rated_bullet_model_n5.RDS"))
